Preliminary stuff

### 2022-11-17 code/process.Rmd
add pred interval

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
theme_set(theme_bw())
```

@@

d_es <-  d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> 
  rowwise() |> 
  mutate(d_calc_target=fill_es(target_ES_type, target_ES_value, target_N)) |> 
  mutate(d_calc_rep=fill_es(replication_ES_type, replication_ES_value, replication_N))

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
library(Replicate)
theme_set(theme_bw())
```

@@

est_SE <- function(p,d){
  z <- -.862+sqrt(abs(.743-2.404*log(p)))
  SE <- abs(d/z)
  return(SE)
}

d_es <-  d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> 
  rowwise() |> 
  mutate(d_calc_target=fill_es(target_ES_type, target_ES_value, target_N),
         se_calc_target=est_SE(target_pvalue,d_calc_target),
         d_calc_rep=fill_es(replication_ES_type, replication_ES_value, replication_N),
         se_calc_rep=est_SE(replication_pvalue,d_calc_rep))

@@

d_es_try <- d_es |> filter(!is.na(d_calc_target)) |> 
  filter(!is.na(d_calc_rep)) |> 
  mutate(
         predInt=Replicate::pred_int(d_calc_target,se_calc_target**2, d_calc_rep, se_calc_rep**2)$rep.inside,
         p_orig=Replicate::p_orig(d_calc_target,se_calc_target**2, d_calc_rep, t2=0, se_calc_rep**2))

# PredInt and P_orig

d_es_try |> ggplot(aes(x=d_calc_target, y=d_calc_rep, color=p_orig))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="p_orig", x="Original SMD", y="Replication SMD")

d_es_try |> mutate(p_sig=p_orig<.05) |> ggplot(aes(x=d_calc_target, y=d_calc_rep, color=p_sig))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)+
  labs(color="P_orig<.05", x="Original SMD", y="Replication SMD")

d_es_try |> ggplot(aes(x=d_calc_target, y=d_calc_rep, color=predInt))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)+
  labs(color="rep in predInt", x="Original SMD", y="Replication SMD")

d_es_try |> ggplot(aes(x=replicated_report_code, y=p_orig))+geom_jitter(height=0, alpha=.5)+
  #scale_y_log10()+
  geom_hline(yintercept=.05)

d_es_try |> ggplot(aes(x=replicated_report_code, y=predInt))+geom_jitter(alpha=.5)
```
